%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.2 (16/9/2014)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 
% TODO:
% 1. Integrate biber/bibtex for article citation under publications.
% 2. Figure out a smoother way for the document to flow onto the next page.
% 3. Add styling information for a "Projects/Hacks" section.
% 4. Add location/address information
% 5. Merge OpenFont and MacFonts as a single sty with options.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% CHANGELOG:
% v1.1:
% 1. Fixed several compilation bugs with \renewcommand
% 2. Got Open-source fonts (Windows/Linux support)
% 3. Added Last Updated
% 4. Move Title styling into .sty
% 5. Commented .sty file.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the
% vertical limit
% 2. Hacky space on the first bullet point on the second column.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\documentclass[]{deedy-resume}
\usepackage{fancyhdr}
\urlstyle{same}

\pagestyle{fancy}
\fancyhf{}
 
\rfoot{Page \thepage \hspace{1pt}}
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{Deric}{Pang}{
    \href{mailto:dericp@cs.washington.edu}{dericp@cs.washington.edu}\\
    \href{https://homes.cs.washington.edu/~dericp}{homes.cs.washington.edu/\textasciitilde{}dericp} 
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 

\subsection{\href{http://www.washington.edu/}{Univ. of Washington}}
\descript{M.S. in Computer Science}
\location{Graduating June 2019 | Seattle}
\href{https://www.cs.washington.edu/}{Allen School of Computer\\
Science \& Engineering}\\
Combined B.S./M.S. Program
\sectionsep

\subsection{\href{http://www.washington.edu/}{Univ. of Washington}}
\descript{B.S. in Computer Science}
\location{Graduating June 2018 | Seattle}
\href{https://www.cs.washington.edu/}{Allen School of Computer\\
Science \& Engineering}\\
Dean's List\\
\location{GPA: 3.77 / 4.0}
\sectionsep

\subsection{\href{https://www.inf.ethz.ch/}{ETH Z\"urich}}
\descript{UW CSE Direct Exchange}
\location{2016 Fall Semester}
\location{Z\"urich, Switzerland}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Links} 
Github: \href{https://github.com/dericp}{\bf github.com/dericp} \\
LinkedIn: \href{https://www.linkedin.com/in/dericp}{\bf linkedin.com/in/dericp}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Coursework}
\subsection{Graduate}
Machine Learning for Big Data\\
Data Mining (ETH)\\
Information Retrieval (ETH)
\sectionsep

\subsection{Undergraduate}
Machine Learning\\
Natural Language Processing\\
Visual Computing (ETH)\\
Algorithms\\
Systems Programming\\
Data Structures \& Parallelism\\
Hardware Software Interface\\
Software Design \& Implementation\\
Human Computer Interaction (ETH)\\
Web Programming

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\subsection{Languages}
Python \textbullet{} Java \textbullet{} C \textbullet{} C++ \textbullet{} Shell\\
Scala \textbullet{} HTML \& CSS \textbullet{} JavaScript\\
PHP \textbullet{} Matlab \textbullet{} \LaTeX\ \\ 
\sectionsep
\subsection{Techs \& Tools}
TensorFlow \textbullet{} MXNet \textbullet{} PyTorch\\
AWS \textbullet{} Git \textbullet{} Ant \textbullet{} Gradle \textbullet{} Kaldi

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.66\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}
\runsubsection{\href{https://www.amazon.com/}{Amazon}}
\descript{| Software Development Engineering Intern}
\location{June 2017 - Sept 2017 | Seattle, WA}
\begin{tightemize}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
    \item Intern in Alexa Machine Learning.
    \item Worked on Amazon's internal deep learning framework specialized for automatic
    speech recognition.
\end{tightemize}
\sectionsep

\runsubsection{\href{http://www.marchex.com/}{Marchex}}
\descript{| Software Engineering/Research Intern}
\location{June 2016 – Sept 2016 | Seattle, WA}
\begin{tightemize}
  \item Built an automatic speech recognition system using deep learning techniques to transcribe phone calls.
  \item Trained a neural network based on the Deep Speech 2 architecture.
  \item Transcribed Australian English with the Kaldi speech recognition toolkit.
\end{tightemize}
\sectionsep

\runsubsection{\href{https://www.amazon.com/}{Amazon}}
\descript{| Software Development Engineering Intern }
\location{Mar. 2016 – June 2016 | Seattle, WA}
\begin{tightemize}
  \item Developed business critical software to validate payment instruments.
  \item Integrated with AWS technologies such as AWS SWF, Lambda, S3, DynamoDB, SQS, and SNS.
\end{tightemize}
\sectionsep

\runsubsection{\href{https://www.cs.washington.edu/}{UW Allen School}}
\descript{| Teaching Assistant}
\location{Winter 2016 – Present | University of Washington}
\begin{tightemize}
  \item TA for CSE 446 Machine Learning (\href{https://courses.cs.washington.edu/courses/cse446/17sp/}{Spring 2017}, \href{https://courses.cs.washington.edu/courses/cse446/17au/}{Fall 2017}) and CSE 331 Software Design \& Implementation (\href{https://courses.cs.washington.edu/courses/cse331/16wi/}{Winter 2016}).
  \item Planned and delivered lectures during weekly recitations.
  \item Graded and provided feedback for weekly programming projects.
  \item Met weekly with the lecturing professor to discuss course progress.
\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     RESEARCH
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Research}
\runsubsection{\href{https://github.com/TellinaTool}{Tellina Tool}}
\descript{| Undergraduate Researcher}
\location{Jan 2017 – June 2017 | UW Allen School}
\begin{tightemize}
\item Advised by \href{https://homes.cs.washington.edu/~mernst/}{Michael Ernst} and
\href{https://www.cs.washington.edu/people/faculty/lsz}{Luke Zettlemoyer}.
\item Worked on a tool to generate bash commands from natural language.
\end{tightemize}
\sectionsep

\runsubsection{\href{https://uwplse.org/}{Programming Languages and Software Engineering Lab}}
\descript{| Undergraduate Researcher}
\location{Mar 2015 – Present | UW Allen School}
\begin{tightemize}
\item Advised by \href{https://homes.cs.washington.edu/~mernst/}{Michael Ernst} and
\href{https://people.cs.umass.edu/~rjust/}{Ren{\'e} Just}.
\item Built an \href{https://github.com/dericp/patch-minimization}{automatic bug finder} using patch minimization and delta debugging techniques.
\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     AWARDS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\section{Awards} 
%\begin{tabular}{rll}
%2014	     & top 52/2500  & KPCB Engineering Fellow\\
%2014	     & 1\textsuperscript{st}/50  & Microsoft Coding Competition, Cornell\\
%2013	     & National  & Jump Trading Challenge Finalist\\
%2013     & 7\textsuperscript{th}/120 & CS 3410 Cache Race Bot Tournament  \\
%2012     & 2\textsuperscript{nd}/150 & CS 3110 Biannual Intra-Class Bot Tournament \\
%2011     & National & Indian National Mathematics Olympiad (INMO) Finalist \\
%\end{tabular}
%\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     PUBLICATIONS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Publications} 
\renewcommand\refname{\vskip -0.8cm} % Couldn't get this working from the .cls file
\bibliographystyle{abbrv}
\bibliography{publications}
\nocite{*}

\end{minipage} 
\end{document}  \documentclass[]{article}
