\documentclass{resume}

% document margins
\usepackage[left=0.75in,top=0.3in,right=0.75in,bottom=0.3in]{geometry}

% name
\name{Deric Pang}

% header
\address{\href{mailto:dericp@cs.washington.edu}{dericp@cs.washington.edu}}
\address{\href{https://dericp.github.io}{https://dericp.github.io}}

\begin{document}

\begin{rSection}{Education}

  {\href{https://www.cs.washington.edu/}
    {\bf University of Washington}} \hfill {June 2019} \\
  M.S. in Computer Science \\
  Thesis: \emph{Improving Natural Language Inference with Syntactic Word Representations}

  \vspace{-0.2em}
  {\href{https://www.cs.washington.edu/}
        {\bf University of Washington}} \hfill {Mar. 2018} \\
  B.S. in Computer Science \\
  Honors: \emph{cum laude} (GPA: 3.79/4.00), \href{https://www.pbk.org/web}
    {Phi Beta Kappa} \\
  \href{https://cra.org/about/awards/outstanding-undergraduate-researcher-award/}
       {CRA Outstanding Undergraduate Researcher Award} (Honorable Mention)

  \vspace{-0.2em}
  {\href{https://www.inf.ethz.ch/}
    {\bf Swiss Federal Institute of Technology in Z\"{u}rich (ETH Z\"{u}rich)}}
    \hfill {Sept. 2016 -- Feb. 2017} \\
  University of Washington Computer Science \& Engineering Direct Exchange

\end{rSection}

\begin{rSection}{Experience}
  \begin{rSubsection}{\href{https://nlp.washington.edu/}
                           {UW Natural Language Processing}}
                     {Jan. 2018 -- June 2019}
                     {Researcher, advised by
                       \href{https://homes.cs.washington.edu/~nasmith/}
                            {Noah Smith}}
                     {University of Washington}
    \item Improved textual inference by incorporating syntactic
      information in neural models.
    %\item Work under review for EMNLP 2019.
  \end{rSubsection}

  \begin{rSubsection}{{\href{https://unity3d.ai/}{Unity Technologies}}}
                      {June 2018 -- Sept. 2018}
                      {Machine Learning Intern}
                      {San Francisco, CA}
    \item Shipped multi-agent curriculum learning in the
      \href{https://github.com/Unity-Technologies/ml-agents}
           {Unity Machine Learning Agents Toolkit}.
  \end{rSubsection}

  \begin{rSubsection}{{\href{http://www.nvidia.com/page/home.html}{NVIDIA}}}
                      {Mar. 2018 -- June 2018}
                      {Applied Research Intern}
                      {Redmond, WA}
    \item Created and investigated methods to train neural networks in
      simulation for autonomous navigation.
    \item Built a rover which was 7\% more autonomous than robots using
      previously published techniques.
  \end{rSubsection}

  \begin{rSubsection}{\href{https://uwplse.org/}
                           {Programming Languages and Software Engineering Lab}}
                     {Mar. 2015 -- Jan. 2018}
                     {Undergraduate Researcher, advised by
                       \href{https://homes.cs.washington.edu/~mernst/}
                            {Michael Ernst},
                       \href{https://www.cs.washington.edu/people/faculty/lsz}
                            {Luke Zettlemoyer},
                       and \href{https://people.cs.umass.edu/~rjust/}
                                {Ren{\'e} Just}}
                     {University of Washington}
  \item Worked on the \href{https://github.com/TellinaTool}{Tellina} project
    \citep{LinWPVZE2017:TR} to generate bash commands from plain English using deep learning.
  \item Created an \href{https://github.com/dericp/patch-minimization}
                        {automatic bug finder}
    using patch minimization and delta debugging techniques
    \citep{PearsonCJFAEPK2017}.
  \end{rSubsection}
  
  \begin{rSubsection}{Alexa Machine Learning ---
                       {\href{https://www.amazon.com/}{Amazon}}}
                     {June 2017 -- Sept. 2017}
                     {Software Development Engineering Intern}
                     {Seattle, WA}
    \item Shipped features in Amazon's internal deep learning framework
      specialized for speech recognition.
    \item Built a system to automatically convert Alexa's acoustic model into
      other deep learning frameworks.
  \end{rSubsection}

  \begin{rSubsection}{\href{http://www.marchex.com/}{Marchex}}
    {June 2016 -- Sept. 2016}{Software Engineering Intern}{Seattle, WA}
  \item Built an automatic speech recognition system based on the Deep Speech 2
    neural network architecture.
  \end{rSubsection}

  \begin{rSubsection}{\href{https://www.amazon.com/}{Amazon}}
                     {Mar. 2016 -- June 2016}
                     {Software Development Engineering Intern}
                     {Seattle, WA}
  \item Used AWS SWF, Lambda, S3, DynamoDB, SQS, and SNS to automatically update
    bank account validation files.
  \end{rSubsection}

  \begin{tabular}{ @{} >{\bfseries}l @{\hspace{3ex}} l }
    Languages: & Python, Java, C, C++, Shell, Scala, HTML \& CSS, JavaScript,
    \LaTeX \\
    Tech/Tools: & PyTorch, TensorFlow, MXNet, AWS, Git, ROS, Unity, D3, Kaldi
  \end{tabular}

\end{rSection}

\begin{rSection}{Publications}
\bibliographystyle{abbrv}
\bibliography{publications}
\end{rSection}

\end{document}
