\documentclass{resume}

% document margins
\usepackage[left=0.75in,top=0.3in,right=0.75in,bottom=0.3in]{geometry}
\usepackage{setspace}

% name
\name{Deric Pang}

% header
\address{pderichai@gmail.com}
\address{\href{https://dericpang.com/}{dericpang.com}}

\begin{document}

\begin{rSection}{Experience}
	\begin{rSubsection}{\href{https://www.figma.com/careers/}
			{Figma}}
		{July 2023 -- Present}
		{Senior Research Engineer}
		{New York, NY}
		\item Lead the modeling and evaluation of new design generation AI features.
		\item Built the LLM finetuning infrastructure used by Figma's machine learning engineers.
		\item Developed the evaluation strategy for new text- and vision-based design search.
	\end{rSubsection}

	\begin{rSubsection}{\href{https://careers.google.com/locations/new-york/}
			{Google}}
		{Sept. 2019 -- July 2023}
		{Senior Software Engineer, Tech Lead}
		{New York, NY}
		\item Worked on semantic parsing and question answering for Google Search.
		\item Tech lead improving Google Search query understanding via distillation from LLMs.
		\item Built a system to mine entity relations from web documents.
	\end{rSubsection}

	\begin{rSubsection}{\href{https://nlp.washington.edu/}
			{UW Natural Language Processing}}
		{Jan. 2018 -- June 2019}
		{Researcher, advised by
			\href{https://homes.cs.washington.edu/~nasmith/}
			{Noah Smith}}
		{University of Washington}
		\item Improved textual inference by incorporating syntactic
		information in neural models \citep{pang2019improving}.
	\end{rSubsection}

	\begin{rSubsection}{{\href{https://unity.com/}{Unity Technologies}}}
		{June 2018 -- Sept. 2018}
		{Machine Learning Intern}
		{San Francisco, CA}
		\item Shipped multi-agent curriculum learning in the
		\href{https://unity.com/products/machine-learning-agents}
		{Unity Machine Learning Agents Toolkit}.
	\end{rSubsection}

	\begin{rSubsection}{{\href{http://www.nvidia.com/page/home.html}{NVIDIA}}}
		{March 2018 -- June 2018}
		{Applied Research Intern}
		{Redmond, WA}
		\item Developed methods of training neural networks in simulation for autonomous navigation.
		\item Built a rover which was 7\% more autonomous than robots using previously published
		techniques.
	\end{rSubsection}

	\begin{rSubsection}{\href{https://uwplse.org/}
			{Programming Languages and Software Engineering Lab}}
		{March 2015 -- Jan. 2018}
		{Researcher, advised by
			\href{https://homes.cs.washington.edu/~mernst/}
			{Michael Ernst},
			\href{https://www.cs.washington.edu/people/faculty/lsz}
			{Luke Zettlemoyer},
			and \href{https://people.cs.umass.edu/~rjust/}
			{Ren{\'e} Just}}
		{University of Washington}
		\item Worked on \href{https://github.com/TellinaTool}{Tellina}, a tool
		to generate bash commands from plain English using deep learning \citep{LinWPVZE2017:TR}.
		\item Created an \href{https://github.com/pderichai/patch-minimization}{automatic bug finder}
		using patch minimization and delta debugging techniques
		\citep{Pearson:2017:EIF:3097368.3097441}.
	\end{rSubsection}

	\begin{rSubsection}{\href{https://www.amazon.jobs/en/teams/alexa-ai/}
			{Amazon Alexa AI}}
		{June 2017 -- Sept. 2017}
		{Software Development Engineering Intern}
		{Seattle, WA}
		\item Shipped features in Amazon's internal deep learning framework specialized for speech
		recognition.
		\item Built a system to automatically convert Alexa's acoustic model into other deep learning
      frameworks.
	\end{rSubsection}

	%   \begin{rSubsection}{\href{http://www.marchex.com/}{Marchex}}
	%     {June 2016 -- Sept. 2016}{Software Engineering Intern}{Seattle, WA}
	%   \item Built an automatic speech recognition system based on the Deep Speech 2
	%     neural network architecture.
	%   \end{rSubsection}

	%   \begin{rSubsection}{\href{https://www.amazon.com/}{Amazon}}
	%                      {March 2016 -- June 2016}
	%                      {Software Development Engineering Intern}
	%                      {Seattle, WA}
	%   \item Used AWS SWF, Lambda, S3, DynamoDB, SQS, and SNS to automatically update
	%     bank account validation files.
	%   \end{rSubsection}

\end{rSection}

\begin{rSection}{Education}
	{\href{https://www.cs.washington.edu/}
		{\bf University of Washington}} \hfill {Sept. 2014 -- June 2019} \\
	B.S. \& M.S. in Computer Science \\
	Thesis: \emph{Improving Natural Language Inference with Syntactic Word Representations} \\
	Honors: \emph{cum laude}, \href{https://www.pbk.org/web}
	{Phi Beta Kappa} \\
	\href{https://cra.org/about/awards/outstanding-undergraduate-researcher-award/}
	{CRA Outstanding Undergraduate Researcher Award} (Honorable Mention)

\end{rSection}

\begin{rSection}{Publications}
	\vspace{1.5em}
	\bibliographystyle{abbrv}
	\bibliography{publications}
\end{rSection}

\end{document}
