\documentclass{resume}

% document margins
\usepackage[left=0.75in,top=0.2in,right=0.75in,bottom=0.3in]{geometry}

% name
\name{Deric Pang}

% header
\address{\href{mailto:dericp@cs.washington.edu}{dericp@cs.washington.edu}}
\address{\href{https://homes.cs.washington.edu/~dericp}{https://homes.cs.washington.edu/\textasciitilde{}dericp}}

\begin{document}

\begin{rSection}{Education}

  {\href{https://www.cs.washington.edu/}{\bf University of Washington, Seattle}} \hfill {Graduating June 2019} \\
  M.S. in Computer Science

  \vspace{-0.2em}
  {\href{https://www.cs.washington.edu/}{\bf University of Washington, Seattle}} \hfill {Sept. 2014 -- Mar. 2018} \\
  B.S. in Computer Science \\
  Honors: \emph{cum laude} (GPA: 3.79/4.00), \href{https://www.pbk.org/web}{Phi Beta Kappa}

  \vspace{-0.2em}
  {\href{https://www.inf.ethz.ch/}{\bf Swiss Federal Institute of Technology in Z\"{u}rich (ETH Z\"{u}rich)}} \hfill {Sept. 2016 -- Feb. 2017} \\
  University of Washington Computer Science \& Engineering Direct Exchange

  % coursework
  \vspace{-0.2em}
  \begin{tabular}{ @{} >{\bfseries}l @{\hspace{3ex}} l }
    Graduate Coursework: & Statistical Methods, Data Mining, Information Retrieval \\ Senior Coursework: & Machine Learning, Natural Language Processing, Data Visualization,\\ & Complexity, Algorithms, Graphics, Visual Computing 
  \end{tabular}

\end{rSection}

\begin{rSection}{Experience}
  \begin{rSubsection}{{\href{https://unity3d.ai/}{Unity Technologies}}}{June 2018 -- Present}{Machine Learning Intern}{San Francisco, CA}
    \item Working on the \href{https://github.com/Unity-Technologies/ml-agents}{Unity Machine Learning Agents Toolkit}.
  \end{rSubsection}

  \begin{rSubsection}{{\href{http://www.nvidia.com/page/home.html}{NVIDIA}}}{Mar. 2018 -- June 2018}{Applied Research Intern}{Redmond, WA}
    \item Investigated practical approaches to training autonomous robots in simulation.
    \item Built an autonomously navigating rover which used a neural network trained only in simulation.
  \end{rSubsection}

  \begin{rSubsection}{\href{http://www.ark.cs.washington.edu/}{Noah's Ark} --- \href{https://nlp.washington.edu/}{UW Natural Language Processing}}
    {Jan. 2018 -- Present}{Researcher, advised by \href{https://homes.cs.washington.edu/~nasmith/}{Noah Smith}}{University of Washington}
    \item Improving natural language inference by incorporating linguistic structure into attention networks.
  \end{rSubsection}

  \begin{rSubsection}{Alexa Machine Learning --- {\href{https://www.amazon.com/}{Amazon}}}{June 2017 -- Sept. 2017}{Software Development Engineering Intern}{Seattle, WA}
    \item Worked on Amazon's internal deep learning framework specialized for automatic
    speech recognition.
    \item Launched a system to translate Alexa's production acoustic model into other deep learning frameworks.
  \end{rSubsection}

  \begin{rSubsection}{\href{https://uwplse.org/}{Programming Languages and Software Engineering Lab}}
    {Mar. 2015 -- Jan. 2018}{Undergraduate Researcher, advised by \href{https://homes.cs.washington.edu/~mernst/}{Michael Ernst}, \href{https://www.cs.washington.edu/people/faculty/lsz}{Luke Zettlemoyer}, and \href{https://people.cs.umass.edu/~rjust/}{Ren{\'e} Just}}{University of Washington}
  \item Worked on the \href{https://github.com/TellinaTool}{Tellina} project \citep{LinWPVZE2017:TR} to generate bash commands from plain English using deep learning.
  \item Created an \href{https://github.com/dericp/patch-minimization}{automatic bug finder} using patch minimization and delta debugging techniques \citep{PearsonCJFAEPK2017}.
  \end{rSubsection}
  
  \begin{rSubsection}{\href{http://www.marchex.com/}{Marchex}}
    {June 2016 -- Sept. 2016}{Software Engineering/Research Intern}{Seattle, WA}
  \item Built an automatic speech recognition system based on the Deep Speech 2 neural network architecture.
  \end{rSubsection}

  \begin{rSubsection}{\href{https://www.amazon.com/}{Amazon}}
    {Mar. 2016 -- June 2016}{Software Development Engineering Intern}{Seattle, WA}
  \item Used AWS SWF, Lambda, S3, DynamoDB, SQS, and SNS to automatically update bank account validation files.
  \end{rSubsection}
\end{rSection}

\begin{rSection}{Skills Summary}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{3ex}} l }
	Languages: & Python, Java, C, C++, Shell, Scala, HTML \& CSS, JavaScript, \LaTeX
	\\ Tech/Tools: & PyTorch, MXNet, TensorFlow, AWS, D3, Git, Ant, Gradle, Kaldi
\end{tabular}

\end{rSection}

\begin{rSection}{Publications}
\bibliographystyle{abbrv}
\bibliography{publications}
\end{rSection}

\end{document}
