%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%   PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage{hyperref}
% document margins
\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry}

% name
\name{Deric Pang}
% email and phone number
\address{dericp@cs.washington.edu}
% github
\address{{\href{https://github.com/pderichai}{https://github.com/pderichai}}}


\begin{document}

%----------------------------------------------------------------------------------------
%   TECHNICAL STRENGTHS SECTION (Renamed)
%----------------------------------------------------------------------------------------

\begin{rSection}{Skills Summary}

	\begin{rQualifications}
		\item Built a production system integrated with AWS  to validate credit card and bank account numbers
		\item Built speech recognition systems using machine learning and language processing techniques
		\item Developed an \href{https://github.com/pderichai/patch-minimization}{automated bug finder} and contributed to multiple research papers in fault localization
	\end{rQualifications}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{3ex}} l }
	Languages: & Java, Python, Shell, JavaScript, HTML \& CSS, PHP, Lua
	\\ Tech/Tools: & AWS, Git, Ant, Gradle, Kaldi, Deep Speech 2, Torch, Apache Storm, AngularJS
\end{tabular}

\end{rSection}


%----------------------------------------------------------------------------------------
%   EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

  {\href{https://www.cs.washington.edu/}{\bf University of Washington, Seattle}} \hfill {Sept. 2014 - Present} \\
  B.S. in Computer Science (Expected Graduation: June 2018) \\
  Dean's List -- Every Quarter \\
  Overall GPA: 3.78/4.00

  {\href{https://www.inf.ethz.ch/}{\bf Swiss Federal Institute of Technology in Z\"{u}rich (ETH Z\"{u}rich)}} \hfill {Sept. 2016 - Present} \\
  University of Washington Computer Science \& Engineering Direct Exchange  \\
  Taking graduate courses in computer science

\end{rSection}

%----------------------------------------------------------------------------------------
%   WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Experience}

  \begin{rSubsection}{\href{http://www.marchex.com/}{Marchex}}
    {June 2016 - Sept. 2016}{Software Engineering/Research Intern}{Seattle, WA}
  \item Built a speech recognition system using deep learning techniques to transcribe phone calls.
  \item Trained a neural network based on the Deep Speech 2 architecture.
  \item Transcribed Australian English with the Kaldi automated speech recognition toolkit.
  \end{rSubsection}

  \begin{rSubsection}{\href{https://www.amazon.com/}{Amazon}}
    {Mar. 2016 - June 2016}{Software Development Engineering Intern}{Seattle, WA}
  \item Developed business critical software in Amazon Payment Services to help validate payment instruments like credit card and bank account numbers.
  \item Integrated with AWS technologies such as AWS SWF, Lambda, S3, DynamoDB, SQS, and SNS.
  \end{rSubsection}

  \begin{rSubsection}{\href{https://uwplse.org/}{Programming Languages and Software Engineering Lab}}
    {Mar. 2015 - Mar. 2016}{Undergraduate Researcher}{University of Washington}
  \item Co-advised by \href{https://people.cs.umass.edu/~rjust/}{Ren{\'e} Just} and \href{https://homes.cs.washington.edu/~mernst/}{Michael Ernst}.
  \item Built an \href{https://github.com/pderichai/patch-minimization}{automated bug finder} using patch minimization and delta debugging techniques.
  \item Co-authored \emph{Evaluating fault localization techniques} -- submitted to \href{http://icse2017.gatech.edu/}{ICSE 2017}.
  \end{rSubsection}
  
  \begin{rSubsection}{\href{https://courses.cs.washington.edu/courses/cse331/16wi/}{CSE 331 -- Software Design and Implementation}}
    {Winter 2016}{Teaching Assistant}{University of Washington}
  \item Planned and delivered lectures during weekly recitations.
  \item Graded and provided feedback for weekly programming projects.
  \item Met weekly with the lecturing professor to discuss teaching, grading, and course progress.
  \end{rSubsection}
  
\end{rSection}


%----------------------------------------------------------------------------------------
%   EXAMPLE SECTION
%----------------------------------------------------------------------------------------

%\begin{rSection}{Section Name}

%Section content\ldots

%\end{rSection}

%----------------------------------------------------------------------------------------

\end{document}
