\documentclass{resume}

% document margins
\usepackage[left=0.75in,top=0.3in,right=0.75in,bottom=0.3in]{geometry}

% name
\name{Deric Pang}

% header
\address{\href{mailto:dericp@cs.washington.edu}{dericp@cs.washington.edu}}
\address{\href{https://homes.cs.washington.edu/~dericp}{https://homes.cs.washington.edu/\textasciitilde{}dericp}}

\begin{document}

\begin{rSection}{Education}

  {\href{https://www.cs.washington.edu/}{\bf University of Washington, Seattle}} \hfill {Graduating June 2019} \\
  Combined B.S./M.S. Program in Computer Science \\
  Paul G. Allen School of Computer Science \& Engineering \\
  Overall GPA: 3.77/4.00 --- Dean's List

  % coursework
  \begin{tabular}{ @{} >{\bfseries}l @{\hspace{3ex}} l }
    Graduate Coursework: & Machine Learning for Big Data, Data Mining, Information Retrieval \\ Senior Coursework: & Machine Learning, Natural Language Processing, Data Visualization,\\ & Algorithms, Graphics, Visual Computing 
  \end{tabular}

\end{rSection}

\begin{rSection}{Experience}

  \begin{rSubsection}{Alexa Machine Learning --- {\href{https://www.amazon.com/}{Amazon}}}{June 2017 -- Sept. 2017}{Software Development Engineering Intern}{Seattle, WA}
    \item Worked on Amazon's internal deep learning framework specialized for automatic
    speech recognition.
    \item Created a system for neural network model translation between deep learning frameworks.
  \end{rSubsection}

  \begin{rSubsection}{\href{https://uwplse.org/}{Programming Languages and Software Engineering Lab}}
    {Mar. 2015 -- Present}{Undergraduate Researcher, advised by \href{https://homes.cs.washington.edu/~mernst/}{Michael Ernst}, \href{https://www.cs.washington.edu/people/faculty/lsz}{Luke Zettlemoyer}, and \href{https://people.cs.umass.edu/~rjust/}{Ren{\'e} Just}}{University of Washington}
  \item Working on the \href{https://github.com/TellinaTool}{Tellina} project to generate bash commands from natural language using deep learning.
  \item Built an \href{https://github.com/dericp/patch-minimization}{automatic bug finder} using patch minimization and delta debugging techniques.
  \end{rSubsection}
  
  \begin{rSubsection}{\href{http://www.marchex.com/}{Marchex}}
    {June 2016 -- Sept. 2016}{Software Engineering/Research Intern}{Seattle, WA}
  \item Built an automatic speech recognition system based on the Deep Speech 2 neural network architecture.
  \item Transcribed Australian English with the Kaldi automatic speech recognition toolkit.
  \end{rSubsection}

  \begin{rSubsection}{\href{https://www.amazon.com/}{Amazon}}
    {Mar. 2016 -- June 2016}{Software Development Engineering Intern}{Seattle, WA}
  \item Worked in Payment Services to automatically validate payment instruments like credit card numbers.
  \item Integrated with AWS technologies such as AWS SWF, Lambda, S3, DynamoDB, SQS, and SNS.
  \end{rSubsection}
  
  \begin{rSubsection}{\href{https://courses.cs.washington.edu/courses/cse446/17au/}{Machine Learning} | \href{https://courses.cs.washington.edu/courses/cse331/16wi/}{Software Design \& Implementation}}
    {Winter 2016 -- Present}{Teaching Assistant for CSE 446 and CSE 331}{University of Washington}
  \item Planned and delivered lectures during weekly recitations.
  \item Graded and provided feedback for weekly programming projects.
  \end{rSubsection}
  
\end{rSection}

\begin{rSection}{Skills Summary}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{3ex}} l }
	Languages: & Python, Java, C, C++, Shell, Scala, HTML \& CSS, JavaScript, PHP, \LaTeX
	\\ Tech/Tools: & TensorFlow, MXNet, PyTorch, AWS, Git, Ant, Gradle, Kaldi
\end{tabular}

\end{rSection}

\begin{rSection}{Publications}
\bibliographystyle{abbrv}
\bibliography{publications}
\nocite{*}
\end{rSection}

\end{document}
