%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%   PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage{hyperref}
% document margins
\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry}

% name
\name{Deric Pang}
% address
\address{4233 9th Ave NE \\ Seattle, WA 98105}
% github
\address{{\href{https://github.com/pderichai}{https://github.com/pderichai}}}
% phone number and email
\address{(702)~$\cdot$~606~$\cdot$~5830 \\ pderichai@gmail.com}

\begin{document}

%----------------------------------------------------------------------------------------
%   EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

  {\bf University of Washington, Seattle} \hfill {September 2014 - Present} \\
  B.S. in Computer Science \& Engineering (Sophomore) \\
  Dean's List \\
  Overall GPA: 3.86/4 \\
  Coursework: Computer Programming I \& II, Foundations of Computing, Hardware Software Interface, Software Design and Implementation

\end{rSection}

%----------------------------------------------------------------------------------------
%   WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Experience}

  \begin{rSubsection}{Undergraduate Researcher}
    {March 2015 -- Present}{University of Washington Computer Science \& Engineering}{Seattle, WA}
  \item Worked as part of the Programming Languages and Software Engineering
    group.
  \item Wrote approximately 3000 lines of code in the summer of 2015.
  \item Studied patch minimization and delta debugging---currently in the process of authoring a paper.
  \end{rSubsection}

  \begin{rSubsection}{Front End Developer}{September 2015}{AT\&T Mobile App Hackathon}{Seattle, WA}
  \item Worked to create \emph{Weelz}, a crowdsourced mobile bike hazard notification android application.
  \end{rSubsection}

  \begin{rSubsection}{Chamber Music Club Officer}{June 2015 -- Present}{Project and Event Planner}{University of Washington}
  \item Arranged members into chamber groups and planned concerts quarterly.
  \end{rSubsection}

\end{rSection}

%----------------------------------------------------------------------------------------
%   PROJECTS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Projects}

  \begin{rSubsection}{Patch Minimizer}{March 2015 -- Present}{}{}
  \item Automatically isolates buggy code between two versions of a program.
  \item Approximately 2000 lines of code.
  \item Can be used with any language or project.
  \end{rSubsection}

  \begin{rSubsection}{\href{https://github.com/pderichai/diff-utils}{Diff-Utils}}{August 2015}{}{}
  \item A diff utility that allows for the syntactically correct manipulation and
    modification of unified diff files.
  \item Created for use in patch minimization research.
  \end{rSubsection}

  \begin{rSubsection}{Weelz}{September 2015}{}{}
  \item A crowd sourced bike hazard notification application.
  \item Worked on front end android application development.
  \end{rSubsection}

\end{rSection}

%----------------------------------------------------------------------------------------
%   TECHNICAL STRENGTHS SECTION (Renamed)
%----------------------------------------------------------------------------------------

\begin{rSection}{Skills}

  \begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
    Proficient In & Java, Linux, Bash \\ Experience With & C, HTML \& CSS,
    JavaScript, Android SDK, Google Maps API \\ Tools & Git, Emacs, Vim, Defects4J
  \end{tabular}

\end{rSection}

%----------------------------------------------------------------------------------------
%   EXAMPLE SECTION
%----------------------------------------------------------------------------------------

%\begin{rSection}{Section Name}

%Section content\ldots

%\end{rSection}

%----------------------------------------------------------------------------------------

\end{document}
