%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%   PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage{hyperref}
% document margins
\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry}

% name
\name{Deric Pang}
% email and phone number
\address{pderichai@gmail.com \\ 1~$\cdot$~(702)~$\cdot$~606~$\cdot$~5830}
% address
\address{C\"{a}sar-Ritz-Strasse 1, Apt. 1602 \\ 8046 Z\"{u}rich, Switerland}
% github
\address{{\href{https://github.com/pderichai}{https://github.com/pderichai}}}


\begin{document}

%----------------------------------------------------------------------------------------
%   EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

  {\bf Swiss Federal Institute of Technology in Z\"{u}rich (ETH Z\"{u}rich)} \hfill {Sept. 2016 - Present} \\
  University of Washington Computer Science \& Engineering Direct Exchange  \\
  Taking master's level courses in computer science

  {\bf University of Washington, Seattle} \hfill {Sept. 2014 - Present} \\
  B.S. in Computer Science \\
  Dean's List \\
  Overall GPA: 3.78/4

\end{rSection}

%----------------------------------------------------------------------------------------
%   WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Experience}

  \begin{rSubsection}{Software Engineering/Research Intern}
    {June 2016 - Sept. 2016}{Marchex}{Seattle, WA}
  \item Utilized machine learning to develop production quality automated speech recognition systems \\ to accurately transcribe phone calls.
  \item Trained a neural network based on the Deep Speech 2 architecture.
  \item Worked with Kaldi to transcribe Australian English.
  \end{rSubsection}

  \begin{rSubsection}{Software Development Engineering Intern}
    {March 2016 - June 2016}{Amazon.com}{Seattle, WA}
  \item Developed business critical software in Amazon Payments to help validate payment instruments.
  \item Utilized AWS technologies such as AWS SWF, Lambda, S3, DynamoDB, SQS, and SNS.
  \end{rSubsection}

  \begin{rSubsection}{Teaching Assistant}
    {Jan 2016 - March 2016}{University of Washington Computer Science \& Engineering}{Seattle, WA}
  \item Worked as a teaching assistant for CSE 331 -- Software Design and Implementation.
  \item Gave weekly lectures and held office hours.
  \end{rSubsection}

  \begin{rSubsection}{Undergraduate Researcher}
    {March 2015 - March 2016}{University of Washington Computer Science \& Engineering}{Seattle, WA}
  \item Co-advised by Ren{\'e} Just and Michael Ernst.
  \item Worked as part of the Programming Languages and Software Engineering group.
  \item Studied patch minimization and delta debugging.
  \item Co-authored a paper titled ``Evaluating Fault Localization Techniques."

  \end{rSubsection}

\end{rSection}


%----------------------------------------------------------------------------------------
%   TECHNICAL STRENGTHS SECTION (Renamed)
%----------------------------------------------------------------------------------------

\begin{rSection}{Skills}

  \begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
    Topics & Machine Learning, Automated Speech Recognition, Distributed Workflows \\
    Technologies & AWS, Kaldi, Deep Speech 2, Torch, Storm, AngularJS \\
    Languages & Java, Python, Bash, Javascript, HTML/CSS, Lua
  \end{tabular}

\end{rSection}

%----------------------------------------------------------------------------------------
%   EXAMPLE SECTION
%----------------------------------------------------------------------------------------

%\begin{rSection}{Section Name}

%Section content\ldots

%\end{rSection}

%----------------------------------------------------------------------------------------

\end{document}
