%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.2 (16/9/2014)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 
% TODO:
% 1. Integrate biber/bibtex for article citation under publications.
% 2. Figure out a smoother way for the document to flow onto the next page.
% 3. Add styling information for a "Projects/Hacks" section.
% 4. Add location/address information
% 5. Merge OpenFont and MacFonts as a single sty with options.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% CHANGELOG:
% v1.1:
% 1. Fixed several compilation bugs with \renewcommand
% 2. Got Open-source fonts (Windows/Linux support)
% 3. Added Last Updated
% 4. Move Title styling into .sty
% 5. Commented .sty file.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the
% vertical limit
% 2. Hacky space on the first bullet point on the second column.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\documentclass[]{deric-pang-resume}
\usepackage{fancyhdr}
 
\pagestyle{fancy}
\fancyhf{}
 
\rfoot{Page \thepage \hspace{1pt}}
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{Deric}{Pang}{\href{mailto:pderichai@gmail.com}{pderichai@gmail.com}} %\\
%\urlstyle{same}\href{https://github.com/pderichai}{https://github.com/pderichai}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 

\subsection{U. of Washington}
\descript{B.S. in Computer Science}
\location{Sept. 2014 - Present | Seattle, WA}
\location{Expected Graduation: June 2018}
Dean's List --- Every Quarter \\
\location{ Cum. GPA: 3.78 / 4.0}
\sectionsep

\subsection{ETH Z\"{u}rich}
\descript{UW Computer Science \& Engineering Direct Exchange}
\location{Sept. 2016 - Present | Switzerland}
Taking graduate CS courses

\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Links} 
Github:// \href{https://github.com/pderichai}{\bf pderichai} \\
LinkedIn://  \href{https://www.linkedin.com/in/pderichai}{\bf pderichai}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Coursework}
\subsection{Graduate}
Data Mining \\
Information Retrieval \\
\sectionsep

\subsection{Undergraduate}
Software Design \& Implementation \\
Data Structures \& Algorithms \\
Hardware Software Interface \\
Functional Programming \\
Computer Graphics + Practicum \\
{\footnotesize \textit{\textbf{(Research Asst. \& Teaching Asst 2x) }}} \\
Unix Tools and Scripting \\

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\subsection{Programming}
\location{Over 5000 lines:}
Java \textbullet{}   Shell \textbullet{} Python \textbullet{} Javascript \\
OCaml \textbullet{} Matlab \textbullet{} Rails \textbullet{} \LaTeX\ \\ 
\location{Over 1000 lines:}
C \textbullet{} C++ \textbullet{} CSS \textbullet{} PHP \textbullet{} Assembly \\
\location{Familiar:}
AS3 \textbullet{} iOS \textbullet{} Android \textbullet{} MySQL
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.66\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}
\runsubsection{Marchex}
\descript{| Software Engineering/Research Intern}
\location{June 2016 - Sept 2016 | Seattle, WA}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Built a speech recognition system using deep learning techniques to transcribe phone calls.
\item Trained a neural network based on the Deep Speech 2 architecture.
\item Transcribed Australian English with the Kaldi automated speech recognition toolkit.
\end{tightemize}
\sectionsep

\runsubsection{Amazon}
\descript{| Software Development Engineering Intern}
\location{June 2014 – Sept 2014 | Mountain View, CA}
\begin{tightemize}
\item Developed business critical software in Amazon Payment Services to help validate payment instruments like credit card and bank account numbers.
\item Integrated with AWS technologies such as AWS SWF, Lambda, S3, DynamoDB, SQS, and SNS.
\end{tightemize}
\sectionsep

\runsubsection{Programming Languages and Software Engineering Lab}
\descript{| Undergraduate Researcher}
\location{Mar 2015 - Mar 2016 | University of Washington}
\begin{tightemize}
\item Co-advised by \href{https://people.cs.umass.edu/~rjust/}{Ren{\'e} Just} and \href{https://homes.cs.washington.edu/~mernst/}{Michael Ernst}.
\item Built an \href{https://github.com/pderichai/patch-minimization}{automated bug finder} using patch minimization and delta debugging techniques.
\item Co-authored \emph{Evaluating fault localization techniques} -- submitted to \href{http://icse2017.gatech.edu/}{ICSE 2017}.
\end{tightemize}
\sectionsep

\runsubsection{CSE 331 -- Software Design and Implementation}
\descript{Teaching Assistant}
\location{Jan 2016 – Mar 2016 | University of Washington}
\begin{tightemize}
\item Planned and delivered lectures during weekly recitations.
\item Graded and provided feedback for weekly programming projects.
\item Met weekly with the lecturing professor to discuss teaching, grading, and course progress.
\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     RESEARCH
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     AWARDS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     PUBLICATIONS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Publications} 
\renewcommand\refname{\vskip -1.5cm} % Couldn't get this working from the .cls file
\bibliographystyle{abbrv}
\bibliography{publications}
\nocite{*}

\end{minipage} 
\end{document}  \documentclass[]{article}
